An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
done with sec 6

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\trimred}{\mathrm{trim}_{{\tt red}}}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
\begin{definition}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
\end{definition}
It turns out that it will be convenient, especially in applications, to allow the target $\ell:\R\to\reals^\Y_+$ to have reports which are ``redundant'' in some sense.
One natural sense is that $\ell$ has a representative set that is a strict subset of $\R$, i.e., $\R$ is not a minimum representative set.
\raft{Some discussion here about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.  BTW, I think their latest version might use different terminology.}
Another is that some reports $r$ are ``dominated'', meaning $r$ is never optimal or there is another report $r'$ which is always optimal when $r$ is optimal.
A priori these alternate definitions may not seem closely related.
In fact, we show in \S~\ref{sec:min-rep-sets} that they are equivalent in our setting.

We now formally introduce the concept of an embedding.
In addition to matching loss values, a key condition for consistency is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\R\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
As ``$L$ has a finite representative set'' is a more succinct condition than ``$L$ is minimizable and $\risk{L}$ is polyhedral'', we will use the former in the sequel.
(Recall that having a finite representative set already implies minimizability.)

@@

  Now suppose $L|_{\R'}$ is non-redundant.
  As $\R'$ is a representative set, Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}) gives some minimum representative set $\Sc \subseteq \R'$.
  Suppose we had some $r \in \R' \setminus \Sc$.
  Now Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
  We conclude $\Sc=\R'$, meaning $\R'$ is a minimum representative set.
\end{proof}

@@

\begin{corollary}\label{cor:trim-loss-red}
  Let $L : \R \to \reals^\Y_+$ have a finite representative set.
  Then $\trimcover(L) = \{L(r) \mid r \in \R,\; \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$.
  % $\mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$
\end{corollary}
\begin{proof}
  \raft{I was a bit surprised how involved this proof ended up being.  Quite possibly there is a faster way, though at the same time, I do like how the proof shows something stronger.  Old version is in before-reorg-sec-3.tex.}
  Let $\A := \{r \in \R \mid \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$.
  We will show the stronger statement, $\A = \bigcup\{\Sc\subseteq\R \mid \Sc \textnormal{ is minimum representative for } L\}$.
  The result will then follow from the definition of trim.

  Let $\Sc$ be a minimum representative set for $L$.
  Observe that $\Gamma_s \not\subseteq \Gamma_{s'}$ for all $s,s'\in\Sc$, $s\neq s'$, as otherwise $\Sc$ would not be minimum representative.
  Furthermore, as $\risk L$ is polyhedral (Corollary~\ref{cor:poly-risk-fin-rep}), Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) together state that for all $r\in\R$, we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
  Let $s\in\Sc$.
  Suppose for a contradiction that $\Gamma_s \subsetneq \Gamma_r$ for some $r\in\R$.
  From the above we have some $s'\in\Sc$ with $\Gamma_r \subseteq \Gamma_{s'}$.
  But now $\Gamma_s \subsetneq \Gamma_r \subseteq \Gamma_{s'}$, contradicting $\Sc$ being minimum representative.
  We conclude that, for all $r\in\R$, either $\Gamma_s = \Gamma_r$ or $\Gamma_s \not\subseteq \Gamma_r$.
  Thus $s\in\A$.

  For the reverse inclusion, let $r\in\A$.
  Let $\Sc$ again be a minimum representative set for $L$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}), we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
  By definition of $\A$, we conclude $\Gamma_r = \Gamma_s$.
  Now take $\Sc' = (\Sc \setminus \{s\}) \cup \{r\}$, that is, the same set of reports with $r$ replacing $s$.
  We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
  As $r\in\Sc'$ we are done.
\end{proof}

@@

We conclude this section with a similar structural result about the properties elicited or embedded by a surrogate.
As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
When working with properties, it is perhaps more natural to define ``trim'' to remove any level sets which are redundant in the sense of set inclusion, as in Corollary~\ref{cor:trim-loss-red}.
Precisely, given a property $\Gamma:\simplex\toto\R$, define
\[ \trimred(\Gamma) := \{\Gamma_r \mid r \in \R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]

With these definitions, we now state a structural result for embeddable properties, and the properties that embed them.
First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
(When working with convex losses, these extra reports are typically the convex hull of the embedded reports.)
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \Theta$.
\end{restatable}

\begin{proof}
  Let $L$ elicit $\Gamma$.
  Observe $L$ is minimizable by definition of elicits.
  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us uniquely determined sets $\V$ and $\Theta$.

  In case 1, in particular $\Gamma$ has a finite representative set $\Sc$, and $\varphi(\Sc)$ is representative for $\gamma$.........
\end{proof}

We defer the proof, and precise definitions, to \S~\ref{app:embed-props}.

>>>>

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\red}{\mathrm{red}}
\newcommand{\trimred}{\mathrm{trim}_\red}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

Several consistent convex surrogates in the literature can be thought of as \emph{embeddings} of the target loss $\ell$, wherein one maps the discrete reports of $\ell$ to a vector space, and finds a convex loss which agrees with the original loss.
A key notion to define an embedding is that of a \emph{representative set}: a set of reports $\Sc$ such that, for all label distributions, at least one report $r\in\Sc$ minimizes expected loss.
\begin{definition}[Representative set]
  Let $\Gamma:\simplex\toto\R$.
  We say $\Sc \subseteq \R$ is \emph{representative for $\Gamma$} if we have $\Gamma(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
  Given a loss $L:\R\to\reals^\Y_+$, we say $\Sc$ is a (minimum) representative set for $L$ if it is a (minimum) representative set for $\prop L$.
  % We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  % We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
\end{definition}
It turns out that it will be convenient, especially in applications, to allow the target $\ell:\R\to\reals^\Y_+$ to have reports which are ``redundant'' in some sense.
One natural sense is that $\ell$ has a representative set that is a strict subset of $\R$, i.e., $\R$ is not a minimum representative set.
\raft{Some discussion here about minimum representative sets and \emph{maximally informative sets} from~\citet{wang2020weston} here, though maybe best to leave it until later.  BTW, I think their latest version might use different terminology.}
Another is that some reports $r$ are ``dominated'', meaning $r$ is never optimal or there is another report $r'$ which is always optimal when $r$ is optimal.
A priori these alternate definitions may not seem closely related.
In fact, we show in \S~\ref{sec:min-rep-sets} that they are equivalent in our setting.

We now formally introduce the concept of an embedding.
In addition to matching loss values, a key condition for consistency is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
\begin{definition}[Embedding]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\R\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
From Corollary~\ref{cor:poly-risk-fin-rep}, $L$ having a finite representative set is an equivalent condition to $L$ being minimizable and $\risk{L}$ being polyhedral.
(Recall that having a finite representative set already implies minimizability.)
As it is also a more succinct condition, we will use the former in the sequel.
In particular, the implications of Lemma~\ref{lem:X} follow whenever $L$ has a finite representative set.

@@

  Now suppose $L|_{\R'}$ is non-redundant.
  As $\R'$ is a representative set, Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}) gives some minimum representative set $\Sc \subseteq \R'$.
  Suppose we had some $r \in \R' \setminus \Sc$.
  Now Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) gives some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$, which contradicts $L|_{\R'}$ being non-redundant.
  We conclude $\Sc=\R'$, meaning $\R'$ is a minimum representative set.
\end{proof}

@@

In fact, we can show something stronger: the reports in minimum representative sets are precisely those which are not strictly redundant.
To formalize this statement, given $\Gamma : \simplex \toto \R$, let $\red(\Gamma) := \{r\in\R \mid \exists r'\in\R,\; \Gamma_r \subsetneq \Gamma_{r'}\}$ be the set of strictly redundant reports.
Similarly, for minimizable $L$, let $\red(L) := \red(\prop L)$.

\begin{proposition}
  Let $L : \R \to \reals^\Y_+$ have a finite representative set.
  Let $\R'$ be the union of all minimum representative sets for $L$.
  Then $\R' = \R \setminus \red(L)$.
  \raft{I was a bit surprised how involved this proof ended up being.  Quite possibly there is a faster way, though at the same time, I do like how the proof shows something stronger.  Old version is in before-reorg-sec-3.tex.}
\end{proposition}

\begin{proof}
  Let $\Gamma = \prop L$.
  Let $\Sc$ be a minimum representative set for $L$, and let $s\in\Sc$.
  Suppose for a contradiction that $s\in\red(\Gamma)$.
  Then we have some $r\in\R$ with $\Gamma_s \subsetneq \Gamma_r$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}) we have some $s'\in\Sc$ such that $\Gamma_r \subseteq \Gamma_{s'}$.
  But now $\Gamma_s \subsetneq \Gamma_r \subseteq \Gamma_{s'}$, contradicting $\Sc$ being minimum representative.
  Thus $\Sc \subseteq \R \setminus \red(\Gamma)$.

  For the reverse inclusion, let $r\in\R\setminus\red(\Gamma)$.
  Let $\Sc$ again be a minimum representative set for $L$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-redundant}), we have some $s\in\Sc$ such that $\Gamma_r \subseteq \Gamma_s$.
  By definition of $\red(L)$, we conclude $\Gamma_r = \Gamma_s$.
  Now take $\Sc' = (\Sc \setminus \{s\}) \cup \{r\}$, that is, the same set of reports with $r$ replacing $s$.
  We have $\{\Gamma_s \mid s\in\Sc\} = \{\Gamma_{s'} \mid s'\in\Sc'\}$, and thus $\Sc'$ is minimum representative for $L$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}).
  As $r\in\Sc'$ we are done.
\end{proof}

As a corollary, we can state another characterization of $\trim$ in terms of redundant reports.
The result follows immediately from the definition of $\trim$.

\begin{corollary}\label{cor:trim-loss-red}
  Let $L : \R \to \reals^\Y_+$ have a finite representative set.
  Then $\trimcover(L) = L(\R \setminus \red(L))$
  % $\{L(r) \mid r \notin \red(\Gamma)\}$.
  % \in \R,\; \forall r'\in\R,\; \Gamma_r = \Gamma_{r'} \textnormal{ or } \Gamma_r \not\subseteq \Gamma_{r'}\}$
  % $\mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$
\end{corollary}

@@

We conclude this section with a similar structural result about the properties elicited or embedded by another property.
We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
In other words, $\Gamma$ embeds $\gamma$ if we have some representative set $\Sc\subseteq\R$ for $\gamma$ and embedding $\varphi:\Sc\to\reals^d$ such that for all $s\in\Sc$ we have $\gamma_s = \Gamma_{\varphi(s)}$.
% The definitions of representative sets and embeddings naturally extend to properties.
% We say a set 
% As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.
Furthermore, when working with properties, it is more natural to define ``trim'' to remove any level sets which are strictly redundant.
Precisely, we define $\trimred(\Gamma) := \{\Gamma_r \mid r \in \R\setminus\red(\Gamma)\}$.
%\R \textrm{ s.t. } \neg\exists r'\in\R,r'\neq r,\, \Gamma_r \subsetneq \Gamma_{r'}\}~.\]

With these definitions, we now state a structural result for embeddable properties, and the properties that embed them.
First, if $\Gamma$ embeds $\gamma$ and $\gamma$ is non-redundant, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$, just with other reports filling in the gaps between the embedded reports of $\gamma$.
When working with convex losses, these extra reports often arise as the convex hull of the embedded reports.
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ elicits $\Gamma$ which embeds $\gamma$, we can think of $L$ as essentially eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with those same level sets.

We will make use of another corollary of Proposition~\ref{prop:embed-iff-trims-equal}, stated for properties.
\begin{corollary}\label{cor:trim-prop-red}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set.
  Then $\trimred(\Gamma)$ is the set of full-dimensional level sets of $\Gamma$.
\end{corollary}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}), for any finite minumum representative set $\Sc\subseteq\R$, the set $\{\Gamma_s\mid s\in\Sc\}$ is exactly the set of full-dimensional level sets $\Theta$ of $\Gamma$.
  From Proposition~\ref{prop:tfae-min-rep-nonredundant}, we have $r \in \R\setminus \red(\Gamma)$ if and only if $r$ is an element of some minimum representative set.
  As $\Gamma$ has at least on minimum representative set, we conclude $\trimred(\Gamma) = \{\Gamma_r \mid r\in \R\setminus\red(\Gamma)\} = \Theta$.  
\end{proof}

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimred(\Gamma)$ is a finite set.%, and $\cup\,\trimred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\hat\Theta$ of $\Gamma$, and $\cup\,\hat\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimred(\gamma) = \trimred(\Gamma) = \{\Gamma_u \mid u\in\U\} = \hat\Theta$.
\end{restatable}

\begin{proof}
  Let $L$ be a fixed loss eliciting $\Gamma$, so that in particular $\risk L$ is fixed.
  Observe $L$ is minimizable by definition of elicits.
  In each case, we will show that $\risk L$ is polyhedral, and thus Lemma~\ref{lem:X} will give us the set $\Theta$ of full-dimensional level sets of $\Gamma$, uniquely determined by $\risk L$.
  In each case we will show that the relevant set of level sets is equal to $\Theta$, giving the result.

  Case 1:
  Let $\Sc$ be the representative set for $\gamma$ and $\varphi:\Sc\to\reals^d$ the embedding.
  Since $\Sc$ is finite, $\varphi(\Sc)$ is a finite representative set for $\Gamma$ (and $L$).
  Corollary~\ref{cor:trim-prop-red} now gives $\trimred(\Gamma) = \Theta$, which is finite, showing Case 2.

  Case 2:
  If $\trimred(\Gamma)$ is finite, then in particular we have a finite set of reports $\Sc \subseteq \R\setminus\red(\Gamma)$ such that $\trimred(\Gamma) = \{\Gamma_s \mid s\in\Sc\}$.
  As $\Gamma$ is elicitable, $\R$ is representative for $\Gamma$.
  By definition of $\trimred$, we have $\simplex = \cup_{r\in\R} \Gamma_r \subseteq \cup \trimred(\Gamma) = \cup_{s\in\Sc} \Gamma_s$, and therefore $\Sc$ is representative for $\Gamma$ and for $L$.
  From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$, showing Case 3.
  Moreover, Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) gives $\{\Gamma_u \mid u\in\U\} = \Theta$.

  Case 3:
  Let $\U$ be a finite minimum representative set.
  Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) once again gives $\{\Gamma_u \mid u\in\U\} = \Theta$.
  We simply let $\hat\Theta = \Theta$, giving Case 4 as $\U$ is representative.

  Case 4:
  Let $\Sc\subseteq\R$ such that $\{\Gamma_s \mid s\in\Sc\} = \hat \Theta$.
  Then $\Sc$ is representative for $\Gamma$ and $L$, as $\cup\hat\Theta = \simplex$.
  Lemma~\ref{lem:loss-restrict} now states that $L$ embeds $L|_\Sc$, so $\Gamma$ embeds $\gamma := \Gamma|_\Sc$, giving Case 1.
  Finally, Corollary~\ref{cor:trim-prop-red} gives $\trimred(\gamma) = \Theta$.
  %
  % Letting $\Theta_\ell$ be the full-dimensional level sets of $\gamma$, Corollary~\ref{cor:trim-prop-red} also gives $\trimred(\gamma) = \Theta'$.
  % From Lemma~\ref{lem:X}(\ref{item:X-rep-contain-min}), we have some minimum representative set $\U\subseteq\U'$ for $L$ and $\Gamma$.
  % We have $\{\gamma_r\mid \varphi(r)\in\U\} = \{\Gamma_u \mid u\in\U\} = \Theta$ by Lemma~\ref{lem:X}(\ref{item:X-min-Theta}) and definition of embedding.
  % As $\Theta$ is a set of full-dimensional level sets of $\gamma$, we must have $\Theta \subseteq \Theta_\ell$.
  % But as $\cup \Theta = \simplex$, we must have $\Theta = \Theta_\ell$, as otherwise there exists $s\in\Sc$ with $\gamma_s \in \Theta_\ell \setminus \Theta$ and thus $\Sc \setminus \{s\}$ would still be representative.
  %
  % 
  % It remains to show $\trimred(\gamma) = \Theta$.
  % Moreover, $\Theta$ is exactly the full-dimensional level sets of $\Gamma$ by Lemma~\ref{lem:X}(\ref{item:X-full-dim}).
  % 
  % From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}) there exists some set of level sets $\Theta'$ which are the full-dimensional level sets of $\gamma$ and there exists a minimum representative set $\Sc\subseteq\R$ with $\{\gamma_s\mid s\in\Sc\} = \Theta'$.
  % Finally, Lemma~\ref{lem:X}(\ref{item:X-redundant}) gives $\trimred(\gamma) = \Theta$.
\end{proof}
